## Chapter 3 Appendix {#sec-3-a}

```{r}
#| label: appendix-3-setup

# Load functions
box::use(
  DBI[dbConnect, dbGetQuery],
  modelsummary[modelsummary]
)
options(modelsummary_format_numeric_latex = "plain")
# Load the models
load("../data/models/study-1-models.RData")
```

### Measures

+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Measure                     | Question                                                                                                                                                                                                                                                                                                  | Coded as                                                                                                                                                           |
+=============================+:=========================================================================================================================================================================================================================================================================================================:+:==================================================================================================================================================================:+
| Age                         | Confirm your age                                                                                                                                                                                                                                                                                          | Text entry                                                                                                                                                         |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Gender                      | What is your gender identity?                                                                                                                                                                                                                                                                             | Non-binary, Female, Male, Prefer not to choose, Other                                                                                                              |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Race                        | Which ethnic or racial category best describes you?                                                                                                                                                                                                                                                       | White, non-Hispanic; Black, non-Hispanic; Hispanic; Asian or Native Hawaiian/other Pacific Islander; Native American/Alaska Native or other race; Multiple races   |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Attention                   | How often do you pay attention to what is going on in government and politics?                                                                                                                                                                                                                            | Always; Most of the time; About half the time; Some of the time; Never                                                                                             |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Dislike Argue               | Do you agree or disagree with the following statement: I dislike arguing about politics.                                                                                                                                                                                                                  | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Enjoy Challenge             | Do you agree or disagree with the following statement: I enjoy challenging the opinions of others.                                                                                                                                                                                                        | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Party ID                    | Generally speaking, do you usually think of yourself as a Democrat, a Republican, an Independent, or what?; Would you say that you are a strong [Republican/Democrat] or not a very strong [Republican/Democrat]?; Do you think of yourself as closer to the Republican party or to the Democratic party? | Republican, Democrat, Independent, Other; Strong, Not very strong; Closer to the Republican party, Neither, Closer to Democratic                                   |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Attn. Check                 | What was the color of the shirt the avatar was wearing?                                                                                                                                                                                                                                                   | I am very certain it was red, I am fairly certain it was red, I am not sure, I am fairly certain it was blue, I am very certain it was blue                        |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Political Prime             | Viewed political attitudes questionnaire before treatment.                                                                                                                                                                                                                                                | 0 = Did not respond to political attitude questionnaire first, 1 = Did respond to questionnaire first                                                              |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Blue Shirt Treatment        | Viewed Blue Shirt or Red shirt                                                                                                                                                                                                                                                                            | 0 = Assigned to red shirt treatment, 1 = Assigned to blue shirt treatment                                                                                          |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Conversation Agree          | Do you agree or disagree with the following statement: I am willing to have a conversation with this person.                                                                                                                                                                                              | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Views Agree                 | Do you agree or disagree with the following statement: I think I would agree about most things with this person.                                                                                                                                                                                          | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Initiate Agree              | Do you agree or disagree with the following statement: I can see myself initiating the conversation with this person.                                                                                                                                                                                     | 1 = Strongly disagree, 2 = Somewhat disagree, 3 = Neither agree nor disagree, 4 = Somewhat agree, 5 = Strongly agree                                               |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Study 1 Measures {#tbl-study-1-measures}

{{< pagebreak >}}

### $H_1$

```{r}
#| label: tbl-ch3-hypothesis-1-main
#| tbl-cap: Full results for reported models in $H_1$
# Redefine names
list_fitted_split_1 <- list(
  "Political Prime" = mod_h1_main
  , "Dislike Arguing" = mod_h1_conflict
  , "Enjoy challenging" = mod_h1_conflict_b
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

### $H_3$

```{r}
#| label: tbl-ch3-hypothesis-2-main
#| tbl-cap: Full results for reported models in $H_1$
# Redefine names
list_fitted_split_1 <- list(
  "Republicans" = mod_h2_dem,
  "Democrats" = mod_h2_rep
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_BlueShirt" = "Blue Shirt"
    , "b_PoliticalPrime:BlueShirt" = "Political Prime $\\times$ Blue Shirt"
    , "b_White" = "White"
    , "b_Education" = "Education"
    , "b_Attention" = "Attention"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-ch3-hypothesis-2-agree
#| tbl-cap: Full results for rep#| orted models in $H_2$ where the outcome is perception of sharing same views
# Redefine names
list_fitted_split_1 <- list(
  "Republicans" = mod_h2_agree_dem,
  "Democrats" = mod_h2_agree_rep
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_BlueShirt" = "Blue Shirt"
    , "b_PoliticalPrime:BlueShirt" = "Political Prime $\\times$ Blue Shirt"
    , "b_White" = "White"
    , "b_Education" = "Education"
    , "b_Attention" = "Attention"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-ch3-hypothesis-2-initiate
#| tbl-cap: Full results for reported models in $H_2$ where the outcome is initiating a conversation
# Redefine names
list_fitted_split_1 <- list(
  "Republicans" = mod_h2_initiate_dem,
  "Democrats" = mod_h2_initiate_rep
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_PoliticalPrime" = "Political Prime"
    , "b_BlueShirt" = "Blue Shirt"
    , "b_PoliticalPrime:BlueShirt" = "Political Prime $\\times$ Blue Shirt"
    , "b_White" = "White"
    , "b_Education" = "Education"
    , "b_Attention" = "Attention"
    , "b_DislikeArgue" = "Dislike Argue"
    , "b_EnjoyChallenge" = "Enjoy Challenge"
    , "b_Intercept" = "Intercept"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: CES"
    , "Coefficients reflect the effect in terms of logged-odds."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```