# Chapter 2 Appendix {#sec-2-a}

```{r}
#| label: setup

# Load helpful functions
box::use(
  modelsummary[
    modelsummary
    , datasummary_skim
  ]
  , data.table[...]
)

# Load fitted models and ppc checks
load(
  file = "../data/temp/models/study_1_fitted.RData"
)
# Load data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../data/clean/cleaned_pavlovia.csv"
)
```

## A note about discrepancies between the main text and the pre-registered report

I posted a pre-registration of my hypotheses [on OSF.](https://osf.io/e9gk8/) The pre-registration allows me to offer transparency about what I expect to find before I analyze any data. This reduces the amount of post-hoc rationalization of any findings pulled from the data. The pre-registered hypotheses are the same as those that are tested here. Despite the similarities between my pre-registered hypotheses and research design, there are a few subtle differences between what I pre-registered and what I ended up doing. In the spirit of complete transparancy, I wanted to make a note of these differences.

Again, the hypotheses that I pre-registered remain the same as what is presented in the main text. The research design also remained the same. During the IRB process, I had to make some decisions about space considerations as I was concerned about participants taking longer than the advertised time (6 minutes). Due to these concerns, I removed some questions. Namely, I no longer asked participants about the color of the yard sign after viewing it nor did I include a battery for political knowledge. These were changes that I made during the IRB process, but did not change in my pre-registered report. In full transparency, mostly because I forgot to make the update as well as having some issues with Dropbox at the time. Removing these questions also had principled reasons. First, I did not want to inflate the treatment effect by asking participants to reflect and tell me the color they saw and then report the partisanship of the candidate. I wanted to get as close to a snap-judgment as I could get and I wanted to immediately ask participants about the partisanship of the candidate after viewing the yard sign to accomplish this goal. For the political knowledge battery, I discuss why I elected to use attention over knowledge in the main text of the chapter. But further, the prevailing questions on political knowledge are suspect as they provide factual information that can be googled participants during the study. Given the length of time it would take for participants to respond to these additional questions and concerns about what value they provide, I did not include them. Those who would like to confirm, I have the IRB materials posted on [my github](https://github.com/DamonCharlesRoberts/color_as_political_information/tree/30508e8f4100c7e19382611fe046ed936c1fdb42/src/assets/irb) which you can see the history of these files.

Another set of discrepancies is some of my modeling strategies. As I note in the main text, some of the data from the mouseview exercise are not exactly what I had expected initially. I do not have much information about the size of the screen participants had nor do I have precise data for when participants were able to view the yard sign during those 5 seconds that it was up. The data for each trial began recording on an instruction screen that I used to standardize cursor starting position and when they finished the trial. As there is a lot of variation between when participants stopped viewing the instructions, I can't be sure which cursor movements were during the display of the yard sign. Because of the noisiness of the mouseview data, I simplified some of my analyses for $H_1$ and $H_4$.

For $H_5$, I had mentioned that I would include an analysis with a synthetic control. However, the district-level data available at the time of writing is not yet available. Because of this, I cannot leverage redistricting patterns for better causal identification of the question of whether campaigns respond to district characteristics or if they anticipate them. Therefore, I stick with the more descriptive task. Relatedly, I had indicated I would use a multilevel model by using intercepts that partially pool at the district level and intercepts that are not pooled at the state level. Upon further reflection on this strategy, this seemed inappropriate for the question at hand as I did not have clear expectations about variation within states but rather more generally was asking a question about districts at large. Further, I did not specify that I would be using a beta regression for these models so many may read my pre-registration as me implying that I would use ordinary least squares. This is totally reasonable. However, out of concern with reporting results that are extremely unstable because of poor choice in estimator as I discuss in the main text and later in the appendix, the ordered beta regression provides more stable results that I am comfortable making inferences with.

## Measures

+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Measure                     | Question                                                                                                                                                                                                                                                                                                  | Coded as                                                                                                                                                           |
+=============================+:=========================================================================================================================================================================================================================================================================================================:+:==================================================================================================================================================================:+
| Age                         | Confirm your age                                                                                                                                                                                                                                                                                          | Text entry                                                                                                                                                         |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Gender                      | What is your gender identity?                                                                                                                                                                                                                                                                             | Non-binary, Female, Male, Prefer not to choose, Other                                                                                                              |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Sex                         | What is your sex assigned at birth?                                                                                                                                                                                                                                                                       | Female, Male, Other                                                                                                                                                |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Race                        | Which ethnic or racial category best describes you?                                                                                                                                                                                                                                                       | White, non-Hispanic; Black, non-Hispanic; Hispanic; Asian or Native Hawaiian/other Pacific Islander; Native American/Alaska Native or other race; Multiple races   |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Color blind                 | Have you been diagnosed with any of the following visual impairments that are not treated with corrective lenses?                                                                                                                                                                                         | Color blindness (any form); Blurred vision (not treatable by corrective lenses); Macular degeneration; Glaucoma; Cataract; Diabetic retinopathy; None of the above |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Attention                   | How often do you pay attention to what is going on in government and politics?                                                                                                                                                                                                                            | Always; Most of the time; About half the time; Some of the time; Never                                                                                             |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Party ID                    | Generally speaking, do you usually think of yourself as a Democrat, a Republican, an Independent, or what?; Would you say that you are a strong [Republican/Democrat] or not a very strong [Republican/Democrat]?; Do you think of yourself as closer to the Republican party or to the Democratic party? | Republican, Democrat, Independent, Other; Strong, Not very strong; Closer to the Republican party, Neither, Closer to Democratic                                   |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Attn. Check                 | In a few words describe what is your first memory of a political event.                                                                                                                                                                                                                                   | Text entry                                                                                                                                                         |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Trial stimuli               | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = White, 1 = Red/Blue                                                                                                                                            |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Trial stimuli alt           | Yard sign assigned                                                                                                                                                                                                                                                                                        | 0 = Not red/blue, 1 = Red/Blue                                                                                                                                     |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Time elapsed                | NA                                                                                                                                                                                                                                                                                                        | Difference between time at start of trial and stop                                                                                                                 |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| $\Delta_{t}$ (milliseconds) | NA                                                                                                                                                                                                                                                                                                        | Time elapsed between cursor movements                                                                                                                              |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| $\Delta_{x}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along x-axis                                                                                                                                |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| $\Delta_{y}$ (pixels)       | NA                                                                                                                                                                                                                                                                                                        | Number of pixels moved along y-axis                                                                                                                                |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Candidate party             | Is this candidate a Republican, a Democrat, or Neither?                                                                                                                                                                                                                                                   | Republican, Democrat, Neither                                                                                                                                      |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Candidate vote              | Of the three candidates who would you most likely vote for?                                                                                                                                                                                                                                               | The first yard sign, The second yard sign, The third yard sign                                                                                                     |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Candidate vote indicator    | NA                                                                                                                                                                                                                                                                                                        | 0 = Would not vote for first yard sign, 1 = Would vote for first yard sign                                                                                         |
+-----------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Study 1 Measures {#tbl-study-1-measures}

{{< pagebreak >}}

## Hypothesis 2

To test whether people associate the color red on a political yard sign with Republicans and the color blue on a political yard sign with Democrats. 


### Models

These first two models are ordered logistic regressions. The outcome of interest is a 3-item response of whether they perceived the owner of the yard sign to be a Republican, a Democrat, or neither. This variable was recoded to be 1 = Democrat, 2 = Independent, and 3 = Republican. In the first ordered logistic regression, I predict this outcome with a indicator variable of whether the participant saw a white yard sign (value of 0) or saw a red yard sign (value of 1). 

My defined priors for the beta coefficient are $Normal(0, 1)$. This means that I think that 68% of the non-transformed beta coefficients I think will be between -1 and 1, with the remaining 32% being larger than that. I fit the models on 4 chains with 2000 chains each (1000 warmup, and 1000 sampled).

@tbl-hypothesis-2-main reports the logged-odds of a subject reporting that a subject was either a Democrat, Independent, or Republican. Positive logged-odds indicate that the logged-odds of a subject reporting a candidate is a Republican increase, whereas a negative value indicate that the logged-odds of reporting the candidate is a Democrat.

```{r}
#| label: tbl-hypothesis-2-main
#| tbl-cap: Full results for reported models in $H_2$
# Redefine names
list_fitted_split_1 <- list(
  "Red treatment" = list_fitted[["h_2"]][["red"]]
  , "Blue treatment" = list_fitted[["h_2"]][["blue"]]
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

I also suspected that these effects could be moderated or sensitive to other things. First @tbl-interacted-models-h-2 reports how these effects in @tbl-hypothesis-2-main may be moderated by age.

```{r}
#| label: tbl-interacted-models-h-2
#| tbl-cap: $H_2$ models moderated by age
# Redefine names
list_fitted_split_2 <- list(
  "Red treatment - Age moderating" = list_fitted[["h_2"]][["red_interact"]]
  , "Blue treatment - Age moderating" = list_fitted[["h_2"]][["blue_interact"]]
)

# Make table
modelsummary(
  list_fitted_split_2
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_age" = "Age"
    , "b_trial_1_red_stimuli:age" = "Red yard sign $\\times$ Age"
    , "b_trial_1_blue_stimuli:age" = "Blue yard sign $\\times$ Age"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

Additionally, I seek to test whether these effects reported in @tbl-hypothesis-2-main are sensitive to the way I chose to test these effects. Specifically, I code the predictor variables as 0 = not red/blue, 1 = red/blue. This gives me two variables that I include in a single ordered logistic regression. This means that the intercept term is the logged-odds of defining the participants as either Democrat, Independent, or Republican if the subject received a white yard sign. The two beta coefficients, in that model reflect the difference in the logged-odds of reporting that the candidate was either a Democrat, Independent, or Republican when they received the red or blue yard sign relative to the white yard sign. The results remain robust to this alternative specification. 

```{r}
#| label: tbl-robustness-alt-specification-h-2
#| tbl-cap: $H_2$ models with alternative specification
# Redefine names
list_fitted_split_3 <- list(
  "Single model" = list_fitted[["h_2"]][["single_model"]]
)

# Make table
modelsummary(
  list_fitted_split_3
  , coef_map = c(
    "b_trial_1_red_stimuli_alt" = "Red yard sign"
    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brakcets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

Finally, I check to see if the results reported in @tbl-hypothesis-2-main are moderated by subjects that are colorblind. Though, I have reasons to beleive they are, the sample does not really lend itself to a robust test of this. The sample does not have a large number of respondents who indicated that they were diagnosed with some type of colorblindness. Therefore, I likely do not have enough data points for colorblind respondents in these different groups. 

```{r}
#| label: tbl-colorblindness
#| tbl-cap: $H_2$ moderated by colorblindness

# Redefine names
list_fitted_split_4 <- list(
  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
)
# Make table
modelsummary(
  list_fitted_split_4
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign $\\times$ Color blind"
    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign $\\times$ Color blind"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

### Posterior Predictive Checks

To check whether my model specification (the variables that I included and the priors I define) are robust, I plot the posterior predictive checks for the model. These posterior predictive checks take the predicted values given my posterior distribution for each of these models, and plots the distribution of these predicted values relative to the distribution of actual values tha I have in my dataset. A well-specified model would show that there are not large nor systematic differences between the distributions of the predicted and actual values. Here, it appears that all of the models do a pretty good job.

```{r}
#| label: fig-h-2-ppc
#| layout-ncol: 2
#| fig-cap: Posterior predictive checks of models in $H_2$
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
#|   - Red treatment (Moderated by age)
#|   - Blue treatment (Moderated by age)
#|   - Single model
#|   - Red treatment (Moderated by colorblindness)
#|   - Blue treatment (Moderated by colorblindness)

list_ppc[["h_2"]][["red"]]
list_ppc[["h_2"]][["blue"]]
list_ppc[["h_2"]][["red_interact"]]
list_ppc[["h_2"]][["blue_interact"]]
list_ppc[["h_2"]][["single_model"]]
list_ppc[["h_2"]][["red_colorblind"]]
list_ppc[["h_2"]][["blue_colorblind"]]
```

## $H_{2a}$

An aditional analysis I include is to examine the bounds by which these effects hold if we vary the amount of partisan colors are on a yard sign. The second and third trials introduce variations of the yard signs in the first trial that include more white and even more color for the opposing political party (if red or blue condition). The goal here is to see whether these results that are reported in @tbl-hypothesis-2-main are weaker for these other two trials.

I specify the exact same models as I did for @tbl-hypothesis-2-main. The only difference is that these variables record responses and treatment assignment for trials two and three. The results that are reported in @tbl-hypothesis-2a and @tbl-hypothesis-2a-cont suggest that my initial suspicions have *some* validity to them. That is, we see that the effects reported in @tbl-hypothesis-2-main are much weaker for blue yard signs -- participants are not as decisive in reporting that the candidate with the blue yard signs are Democrats. The effects reported in @tbl-hypothesis-2-main seem to hold for the red yard signs, however. Like before, I examine whether these results are robust to an alternative model specification (a single model with two treatment indicator variables). Like with tests of $H_2$, it appears that they are.

### Models

{{< pagebreak >}}
\blandscape

```{r}
#| label: tbl-hypothesis-2a
#| tbl-cap: Full results for models testing bounds of $H_2$
# Redefine names
model_names <- list(
  "Trial 2 - Red treatment" = list_fitted[["h_2a"]][["trial_2_red"]]
  , "Trial 2 - Blue treatment" = list_fitted[["h_2a"]][["trial_2_blue"]]
  , "Trial 2 - Single model" = list_fitted[["h_2a"]][["trial_2_single_model"]]
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_2_red_stimuli" = "Red yard sign"
    , "b_trial_2_blue_stimuli" = "Blue yard sign"
    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

```{r}
#| label: tbl-hypothesis-2a-cont
#| tbl-cap: Full results for models testing bounds of $H_2$ (cont.)
# Redefine names
model_names <- list(
  "Trial 3 - Red treatment" = list_fitted[["h_2a"]][["trial_3_red"]]
  , "Trial 3 - Blue treatment" = list_fitted[["h_2a"]][["trial_3_blue"]]
  , "Trial 3 - Single model" = list_fitted[["h_2a"]][["trial_3_single_model"]]
)

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_3_red_stimuli" = "Red yard sign"
    , "b_trial_3_blue_stimuli" = "Blue yard sign"
    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

\elandscape
{{< pagebreak >}}

### Posterior Predictive Checks

To confirm that my models return predicted values from the posterior distribution that reflect my actual data, I plot the posterior predictive checks for each model. All six models appear to do a pretty good job.

```{r}
#| label: fig-h-2a-ppc
#| layout-ncol: 2
#| fig-cap: Posterior predictive checks of models in $H_2$
#| fig-subcap:
#|   - Red treatment (Trial 2)
#|   - Blue treatment (Trial 2)
#|   - Combined model (Trial 2)
#|   - Red treatment (Trial 3)
#|   - Blue treatment (Trial 3)
#|   - Combined model (Trial 3)

list_ppc[["h_2a"]][["trial_2_red"]]
list_ppc[["h_2a"]][["trial_2_blue"]]
list_ppc[["h_2a"]][["trial_2_single_model"]]
list_ppc[["h_2a"]][["trial_3_red"]]
list_ppc[["h_2a"]][["trial_3_blue"]]
list_ppc[["h_2a"]][["trial_3_single_model"]]
```

{{< pagebreak >}}

## Hypothesis 3

### Models

Here, I am testing whether candidates with red yard signs are supported more by Republican subjects and whether candidates with blue yard signs are supported more by Democratic subjects. In my original study, I ask participants after all three trials to report which of the three yard signs they would vote for. Here, I recode this response to be a binary outcome -- would they vote for the first yard sign they saw (value of 1) or not. Like I have done in previous tests, I run two models -- each where the predictor is a indicator of whether they received the red/blue treatment (value of 1) or the white treatment. Since the outcome is dichotomous, instead of an ordered logistic regression, I instead run a logistic regression. Since partisan identification is a primary part of the inferential task here and since it cannot be experimentally treated, I need to control for some confounds such as attention to politics, age, gender identification, and racial identity.

@tbl-h-3-main reports the results of these models. The results suggest that Republicans are indeed more supportive of candidates using the color red, not supportive of candidates using the color blue, and are not supportive of candidates using the color white. The results also suggest that Democrats are more supportive of candidates of using the color blue, and are much less supportive of candidates using the colors red or white. 

```{r}
#| label: tbl-h-3-main
#| tbl-cap: Support of candidate based on partisanship

# Redefine names
model_names <- list(
  "Red stimuli" = list_fitted[["h_3"]][["red"]]
  , "Blue stimuli" = list_fitted[["h_3"]][["blue"]]
)

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_attention" = "Attention"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

{{< pagebreak >}}

### Posterior predictive Checks

To confirm that these models return sensical predictions, I again plot the posterior predictions. @fig-h-3-ppc seems to suggest that both models do a pretty good job at returning a distribution fo predicted outcomes in terms of differences between those values and outcomes measured in my sample.

```{r}
#| label: fig-h-3-ppc
#| layout-ncol: 2
#| fig-cap: Posterior Predictive checks for $H_3$ models
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
list_ppc[["h_3"]][["red"]]
list_ppc[["h_3"]][["blue"]]
```

{{< pagebreak >}}

## Hypothesis 4

$H_4$ seeks to test whether partisan subjects spend more time looking at the yard sign of political opponents than those they share a partisan identity with. Specifically, it seeks to see whether the elapsed time for the trials are longer for participants assigned to a red or blue yard sign condition if the subject is a Democrat or Republican (respectively) relative to Republicans or Democrats (respectively).

The outcome variable is a count of how many milliseconds a respondent was in a given trial. As this is count data, I have high suspicion of over-dispersion (meaning that the mean value and the median value are unequal). To make sure that I am correct in this, I generate a table reporting the summary statistics of the time elapsed in @tbl-h-4-dispersion.

```{r}
#| label: tbl-h-4-dispersion
#| tbl-cap: Checking for over-dispersion of data
df_over_dispersed <- list_df[["cleaned"]][, c("trial_1_time_elapsed")]
names(df_over_dispersed)[names(df_over_dispersed) == 'trial_1_time_elapsed'] <- 'Time Elapsed'
datasummary_skim(
  df_over_dispersed
  , notes = "Data source: Prolific sample."
  , histogram = FALSE
)
```

It appears that there is some over-dispersion here. Therefore, my choices for which type of count model to use leans away from the poisson regression and onto something like a poisson-gamma model. 

### Models

As mentioned above, the outcome here is the time elapsed for a trial (in milliseconds). Since this is a count outcome, I should be using a type of model that uses a link function in the poisson family as opposed to the exponential family. As @tbl-h-4-dispersion demonstrated, the data are over-dispersed. Therefore, I use a poisson-gamma model as my link function which is often referred to as a negative binomial regression. I still have priors suggesting that my beta coefficients are $Normal(0, 1)$. 

Like I have done before, I run two models. One for each partisan stimuli with the baseline category as the White yard sign condition. As the hypothesis goes beyond saying that I think subjects in the red/blue treatment will spend more time looking at the yard sign than in the white, but instead say that I think this will be moderated by partisanship, I include a interaction term in each of these models. Additionally, as partisan identification is a key explantory variable here and is not experimentally treated, I control for a numbe of potential confounds such as attention to politics, age, gender identity, and racial identity. The results of these models are recorded in @tbl-h-4.

```{r}
#| label: tbl-h-4
#| tbl-cap: The effect of partisan congruency on time spent looking at a yard sign
# Redefine names
model_names <- list(
  "Red stimuli" = list_fitted[["h_4"]][["red"]]
  , "Blue stimuli" = list_fitted[["h_4"]][["blue"]]
)

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_attention" = "Attention"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

{{< pagebreak >}}

### Posterior Predictive Checks

As I made a modeling choice based on the overdispersion of the outcome variable, I want to confirm that these models did an adequate job at returning predicted values based on my posterior distribution relative to the actual data in the sample. The posterior predictive checks suggest that it did indeed do a pretty good job. It looks like I may be slightly underestimating some lower values for the elapsed time, but the distribution on the whole looks pretty good -- including on the tails.

```{r}
#| label: fig-h-4-ppc
#| layout-ncol: 2
#| fig-cap: Posterior predictive checks of $H_4$ models
#| fig-subcap:
#|   - Red
#|   - Blue
list_ppc[["h_4"]][["red"]]
list_ppc[["h_4"]][["blue"]]
```

## Hypothesis 5

For $H_5$, I am interested in examining whether or not districts that lean towards one party more than the other have candidates use more of the color in line with the party that has a historical advantage and less of the color for the party that tends to suffer electorally speaking.

### Models

<!-- 
NOTE TO SELF





NEED TO REWRITE SOME OF THIS TO ACCOUNT FOR BETTER PERFORMANCE AFTER LOCATION-FXS
-->

As I mention in the main text of the book, I note that I regress the 5-year rolling average of the democratic vote share in a state upon the proportion of the color red and blue on the yard signs downloaded from the Center for American Political Design. The outcome is a continous and bounded variable between the value of 0 and 1. I note in the main text that I use a ordered beta regression, but here I provide more specifics. As the outcome is continuous but bounded between 0 and 1, treating the outcome variable as a continous variable with no finite bounding as I would with a OLS would be inappropriate. To ensure that I am using the most appropriate estimator to explain the outcome of interest, I elect to use an ordered beta regression. Beta regression models are a type of distributional model that essentially tries to model the distribution of the outcome variable. The standard beta regression model can fit models where the outcome is (0, 1). However, my outcome is [0, 1). I could elect to use a zero-inflated beta regression which would allow me to appropriately model this outcome. However, @kubinec_2022_pa demonstrates that the ordered beta regression is a much more efficient and accurate (in terms of a number of various metrics) approach to dealing with outcomes that can equal either 0 or 1. 

The default priors for $\beta_i$ is $N(0, 5)$ in the $ordbetareg$ [@kubinec_2022_pa] package that I use to fit the model. However, I receive warnings indicating that there are divergent transitions. For HMC, divergent transitions indicate that the sampler is having problems with the curvature of your posterior distribution. As I note in the main text of the book, I am using a multilevel model that includes a partially pooled parameter for the districts and use two non-pooled parameters for the state and the election year. This is a pretty complex problem. Especially givent the estimator that I am using here. More troubling still is that my $\hat{R}$ values are not equal to 1 for either model. These two things together suggest that there is a pretty serious problem and that my posterior distributions are quite unstable.

To try to fix this issue, I adjust the prior for $\beta_1$ to $N(0, 2)$. While I still receive a warning about divergences in both models, the number of them drops down to about 30 out of 4000. Additionally the $\hat{R}$ values are at 1. Together, these tell me that these priors likely helped the models quite a bit and feel more confident in the stability of my model. @tbl-hypothesis-5 presents the results of this second specification of the model.

```{r}
#| label: tbl-hypothesis-5
#| tbl-cap: The effect of democratic vote share on color choices for yard sign

names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_intercept" = "Intercept"
    , "b_dem_vote_share" = "Democratic vote share (%)"
  )
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

### Posterior predictive checks

```{r}
#| label: fig-hypothesis-5-ppc
#| layout-ncol: 2
#| fig-cap: Posterior Predictive checks for $H_5$
#| fig-subcap:
#|   - Proportion of yard signs red
#|   - Proprotion of yard signs blue

list_ppc[["h_5"]][["red"]]$continuous
list_ppc[["h_5"]][["blue"]]$continuous
```